Open Clusters Characterization in Gaia DR2 Using ML Algorithms

### 2020-11-09 thesis/thesis.tex
thesis: Update structure

However, in general it is not as easy and becomes necessary to consider other parameters such as distances, or even
metallicity and age (derived from isochrone curves) and requires photometric data from stars in the studied field.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_ngc_2682.pdf}
    \caption{Proper motions}
    \label{fig:pm_ngc_2682}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/isochrone_ngc_2682.pdf}
    \caption{Isochrone curve}
    \label{fig:parallax_ngc_2682}
  \end{subfigure}
  \caption{Open Cluster NGC 2682}
\end{figure}

@@

@@

>>>>

Figure \ref{fig:pm_melotte_22} shows the proper motion distribution in right ascension and declination.
It is easy to see that a subgroup can be located at [20, -45].
Figure \ref{fig:pm_vec_melotte_22} shows the parallax density and confirms an overdensity at $\approx 7.5 mas$ corresponding to Mellote 22 OC.

However, as shown in Figures \ref{fig:pm_ngc_2682} and \ref{fig:parallax_ngc_2682}, in general it is not as easy and
becomes necessary to consider other parameters such as distances, or even metallicity and age (derived from isochrone curves)
and requires photometric data from stars in the studied field.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_ngc_2682.pdf}
    \caption{Proper motions}
    \label{fig:pm_ngc_2682}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/parallax_ngc_2682.pdf}
    \caption{Parallax}
    \label{fig:parallax_ngc_2682}
  \end{subfigure}
  \caption{Open Cluster NGC 2682}
\end{figure}

@@

% TODO: Hablar de cómo funciona el descargador y cómo está formada la base de datos

\section{Soft Clustering with K-Means}

% TODO: Describir cómo funciona el clustering con KMedias

\section{Deep Embedded Clustering}

% TODO: Describir cómo funciona el clustering usando dec

\section{Results}

@@

\pagebreak
